Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
polish first two paragraph ellis

We decided to attemp to replicate one of the results presented on Fig.14 of their paper \cite{rockstuhl2005}:
the scattering cross-section of a SiC rectangular cylinder for three different aspect ratios. 
To comply with our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
dimension of the geometry), we chose the particular case where a=672 nm and b=328 nm.

@@

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to obtain regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using Python scripts,
and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
as a factor that introduces extra peaks on the response. We were unable to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. 
For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod}.
Figure \ref{fig:tri_reg_round_14} shows the 
results of the effect of uniformity and roundness. One can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results in Rockstuhl et al.

@@

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We obtained data from Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main peaks presented in Rockstuhl et al.\ are 
successfully replicated. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.

@@

 %%% Ellis work summary %%%%
The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
resonant modes in localized surface phonon-polariton nanostructures. They study the
excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
width ($W=400$ nm) and varied length ($L=400-4800$ nm) and therefore an aspect ratio
($AR=L/W=1-12$). These pillars are patterned on a squared grid with a pitch $P=L+500$ nm
to reduce coupling. In  both their simulations and experiments they excite the localized SPhP
resonances, they perform polarized reflectance measurements with the incident polarization 
oriented parallel or perpendicular to the long axis of the pillars.  
 %%% Ellis work summary %%%%

We aim to replicate the computational result presented in Figure S4 of their supplementary 
material (NOT SURE HOW TO CITE THIS) that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We first attempted to replicate this result since they have results where the gap between pillars 
is 5000 nm (10 times more than in the experiments and other simulations on the paper), and 
this diminishes the effects of coupling. This result is suitable to compare with 
what we can model using \pygbe.

@@

\textit{mesh}
For the case of aspect ratio $AR=4$ we count with a triangular surface mesh provided by the authors of 
Ellis et al. Which is a non-structured (HOW IS IT CALLED WHEN IS FINER WHER THERE ARE CORNERS?) mesh of
approximately four thousand elements. To produce the remaining 
meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
uniform mesh, we needed approximately double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
I'M NOT SURE IF WE WANT TO PUT THEM).
To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.

@@

 Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
 A key element is professional software management and engineering, and the central technology solution is version control. 
 Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \citep{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.

>>>>

We decided to attempt to replicate one of the results presented on Fig.14 of their paper \cite{rockstuhl2005}:
the scattering cross-section of a SiC rectangular cylinder for three different aspect ratios. 
To comply with our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
dimension of the geometry), we chose the particular case where a=672 nm and b=328 nm.

@@

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to obtain regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using Python scripts,
and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
as a factor that introduces extra peaks on the response. We were unable to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. 
(For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod})
Figure \ref{fig:tri_reg_round_14} shows the 
results of the effect of uniformity and roundness. One can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results in Rockstuhl et al.

@@

Once we have found the ``best'' possible geometry construction, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We have obtained Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}: the main peaks presented in Rockstuhl et al.\ are 
successfully replicated. While we still have the presence of a third peak in our results, we conjecture 
that this is a consequence of the 3D effects in our geometry.

@@

 %%% Ellis work summary %%%%
The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
resonant modes in localized surface phonon-polariton nanostructures. They study the
excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
and computing polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
width ($W=400$ nm) and varied length ($L=400-4800$ nm). These pillars are patterned on a squared 
grid with a pitch $P=L+500$ nm to reduce coupling. In both their simulations and experiments they 
perform polarized reflectance measurements with the incident polarization 
oriented parallel or perpendicular to the long axis of the pillars.  
 %%% Ellis work summary %%%%

We first aim to replicate the computational result presented in Figure S4 of their supplementary 
material that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
a good candidate to replicate using \pygbe.

@@

\textit{mesh}
For the case of aspect ratio $AR=4$ we count with a triangular surface mesh provided by the authors of 
Ellis et al. Which is a non-uniform mesh of
approximately four thousand elements. To produce the remaining 
meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
uniform mesh, we needed approximately double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
I'M NOT SURE IF WE WANT TO PUT THEM).
To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.

@@
